Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-06-11 Manuscript/proto-manuscript.tex

Simulations with molecular mechanics models represent nuclei as classical particles 
and describe their interactions through a pariwise additive empirical potential \cite{SOME_review, FF_papers}. 
According to the electronic continuum correction (ECC), electrons that surround 
the nuclei shall be taken into account in such simulations as an electronic continuum. \cite{leontyev11}
Such a continuum responds to the electrostatic interactions of the explicitly represented nuclei
as a polarizable dielectric. 
The dielectric constant of shuch a dielectric medium, $\epsilon _{el}$, will 
then resduce the electrostatic interactions in between the nuclei. 
This can be formally represented in classical simulations through scaling of charges of particles with a factor $f_q = \epsilon _{el} ^{-1/2}$. 
Note that the high frequency dielectric constant, which is experimentally measurable \cite{some_original_work, leontyev11}, represents
the part of dielectric response only due to electrons, and it is approximately $\epsilon _{el} ~ 2$ for almost any biomaterial that is
usually simulated/exists in a living cells \todo{choose between the two options}.
The high frequency dielectric constant of water, 
the most abundant molecule in any simulaiton in biophysics, 
is $\epsilon _{el} = 1.78$, hence the scaling factor adopts the value of $f_q = 0.75$. \cite{some_orig_source, leontyev11}

@@

The optimal value for $f_q$ was found by matching the overall membrane structure, 
scattering form factors to the experimental data.
This ensures that the presented model describes the membrane strucutre correctly,
adopts correct liquid disordered phase, 
and provides area per lipid agreeing with experiments (see Fig~\ref{simVSexpNOions} and Table~\ref{tab:apls}).

@@

%Reiterate what we did...
We present models of POPC and DPPC lipids that for the first time exhibit accurate headgroup order parameter response to cation binding. 
The models are derived from Lipid14 model \cite{dickson14} by applying the electronic continuum correction. 
The models were optimized to represent correct membrane structure, 
and they were validated with the use of electrometer concept \cite{seelig87,Altenbach84}. 
Compared to the phenomenological observations of calcium:POPC stoichiometry in the experimental work \cite{Altenbach87}, 
our simulations reveal the same stoichiometry of 2~POPC molecules per 1~calcium but through direct observation. 
This tells us on the subtle effects of calcium in phospholipid membranes 
possibly leading to a better understanding of their physical properties (elasticity etc.). 
\todo{Improve this concluding-discussion with actual insights.}

>>>>

Simulations with molecular mechanics models represent nuclei as classical particles 
and describe their interactions through a pariwise additive empirical potential \cite{SOME_review, FF_papers}. 
According to the electronic continuum correction (ECC), electrons that surround 
the nuclei shall be taken into account in such simulations as an electronic continuum. \cite{leontyev11}
Such a continuum responds to the electrostatic interactions of the explicitly represented nuclei
as a polarizable dielectric. 
The dielectric constant of shuch a dielectric medium, $\epsilon _{el}$, will 
then resduce the electrostatic interactions in between the nuclei. 
This can be formally represented in classical simulations through scaling of charges of particles with a factor $f_q = \epsilon _{el} ^{-1/2}$. 
Note that the high frequency dielectric constant, which is experimentally measurable \cite{some_original_work, leontyev11}, represents
the part of dielectric response only due to electrons, and it is approximately $\epsilon _{el} \approx 2$ for almost any biomaterial that exists in living cells. 
The high frequency dielectric constant of water, 
the most abundant molecule in any cell, 
is $\epsilon _{el} = 1.78$, hence the scaling factor adopts the value of $f_q = 0.75$. \cite{some_orig_source, leontyev11}

@@

The optimal value for $f_\sigma$ was found by representing the overall membrane structure well
by matching scattering form factors to experimental data~\cite{Petrache06, Kucerka08, Pabst10}.
This ensures that the presented model describes correctly the membrane strucutre,
adopts a liquid disordered phase, 
and provides area per lipid agreeing with experiments (see Fig~\ref{simVSexpNOions} and Table~\ref{tab:apls}).

@@

%Reiterate what we did...
We present models of POPC and DPPC lipids that for the first time exhibit accurate headgroup order parameter response to cation binding. 
The models are derived from Lipid14 model \cite{dickson14} by applying the electronic continuum correction. 
The models were optimized to represent correct membrane structure, 
and they were validated with the use of electrometer concept \cite{seelig87,Altenbach85,Altenbach84}. 
Compared to the phenomenological observations of calcium:POPC stoichiometry in the experimental work \cite{Altenbach84}, 
our simulations reveal the same stoichiometry of 2~POPC molecules per 1~calcium but through direct observation. 
This tells us on the subtle effects of calcium in phospholipid membranes 
possibly leading to a better understanding of their physical properties (elasticity etc.). 
\todo{Improve this concluding-discussion with actual insights.}
